Untitled

### 2018-08-02 MSOAmodel.Rmd
Update distrib compare
Trying to make the generation of random bootstraps faster and prevent crashing

test2 <- DistribCompareBootstrapper2(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes, GroupVars = "MSOA11CD" )

@@

```{r}
setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities2")

@@

   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes, GroupVars = "MSOA11CD" )%>%
      saveRDS(., file = paste0(.x, ".rds"))
      }) 
  }

@@

BootDeets <- BootStrapRES %>% 
  map_df(~.x %>%
           mutate(Reference = MedianHomes < MedianLUPs,
                  MeanPropPrice = (HomesValue+LowUseValue)/(Homes+LowUse)) %>%
           select(MSOA11CD, MeanPropPrice, Reference, ID)) %>%
  left_join(select(IncomeEst, MSOA11CD, Yearly.income), by = "MSOA11CD") %>%
  left_join(MSOAdep, by = "MSOA11CD") %>%
  mutate(AffordRatio  = MeanPropPrice/Yearly.income,
         AffordRatio2 = AffordRatio^2,
         AffordRatio3 = AffordRatio^3)

@@

@@

>>>>

test2 <- DistribCompareBootstrapper(BirminghamDATA, 1983, 100, type = NULL, PropertyTypes, GroupVars = "MSOA11CD" )

@@

```{r}
PropertyTypes <- c("D", "S", "T", "F")
setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities2")

@@

   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes, GroupVars = "MSOA11CD" )%>%
      saveRDS(., file = paste0(.x, ".rds"))
      gc()
      }) 
  }

    if(length(newLADsnames)>0){
    for (.x in newLADs) {print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes, GroupVars = "MSOA11CD" )%>%
      saveRDS(., file = paste0(.x, ".rds"))
      gc()
      } 
  }

@@

BootDeets <- BootStrapRES %>% 
  map_df(~.x %>%
           mutate(Reference = HighVal>(LowUse-HighVal),
                  MeanPropPrice = (HomesValue+LowUseValue)/(Homes+LowUse)) %>%
           select(MSOA11CD, MeanPropPrice, Reference, ID)) %>%
  left_join(select(IncomeEst, MSOA11CD, Yearly.income), by = "MSOA11CD") %>%
  left_join(MSOAdep, by = "MSOA11CD") %>%
  mutate(AffordRatio  = MeanPropPrice/Yearly.income,
         AffordRatio2 = AffordRatio^2,
         AffordRatio3 = AffordRatio^3)

@@

CoeffsMega %>%
  ggplot(aes(x = term))

@@

Need to find MSOA that contain 100% of the LSOA of a ward

  StrappedLowUse <- function(WhichLowUse, Grouping){
    Tempdf<- unique(dfWard$LSOA11CD) %>%
          map_df(~{
            #print(.x)
            PriceData <- dfPrice %>% 
              filter(LSOA11CD == .x)
            #Sometimes an LSOA will have no sales in that year. In these thankfully rare cases the entire LAD is used.
            if(nrow(PriceData)==0){
              PriceData<-dfPrice
            }
            LowUseCounts <- sum(filter(dfWard, LSOA11CD == .x) %>% select_(WhichLowUse)) #sample rows from LSOA

            SampledData <-sample_n(PriceData, LowUseCounts*samples, replace = TRUE) %>%
              mutate(ID = rep(1:samples, nrow(.)/samples))

            SampledData
          }
          )

    Tempdf %>% 
      group_by(ID) %>%
      mutate(LADmedian = median(Price, na.rm = T),
             LADmean = mean(Price, na.rm = T)) %>%
      group_by_(.dots = c("ID", Grouping)) %>%
      summarise(Counts = n(),
                Value = sum(Price),
                GeogMedian = median(Price),
                GeogMean = mean(Price),
                LADmedian = first(LADmedian),
                LADmean = first(LADmean)) %>%
      ungroup

  }

dfWardHomesStrap1 <- StrappedLowUse("LowUse", Grouping = "MSOA11CD")

### 2018-08-02 PaperCode.Rmd
Update distrib compare
Trying to make the generation of random bootstraps faster and prevent crashing

@@

```{r}
list.files()

@@

```{r}
#ward folder
setwd(SemiLondon)

wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)

#TowerHamlets
TowerLONDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
  filter(!is.na(DiscClass)) %>%
  group_by(Ward, DiscClass) %>%
  summarise(count = n()) %>% ungroup %>%
  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
  slice(c(1:13, 15:17, 14, 18:20)) %>%
   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
  SemiDataStructure

HaveringLONDATA <- read_excel("AIR12965P Informatiion provided by Council Tax.xlsx" ) %>%
  rename(DiscClass = X__1) %>%
  select(-Mawneys, -`Aveley & Uplands`, -Whalebone) %>%
  gather(key = "ward", value = "counts", -DiscClass) %>%
  spread(key= DiscClass, value = counts, fill = 0) %>%
  mutate(Empty = rowSums(.[,c(5:6,14,17)]), LowUse = Empty+ `Second Home Class A`+ `Second Homes Class B`) %>% 
  bind_cols(., wardnames %>% filter(grepl("Havering", LAD11NM))) %>%
  SemiDataStructure

>>>>

Do the CalcLowUse and ProcessDataMeanPrice functions need to be changed from LSOA to MSOA?

@@

@@

```{r}
# #ward folder
# setwd(SemiLondon)
# 
# 
# wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)

#These don't work now the LSOA are being used directly
# 
# #TowerHamlets
# TowerLONDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
#   filter(!is.na(DiscClass)) %>%
#   group_by(Ward, DiscClass) %>%
#   summarise(count = n()) %>% ungroup %>%
#   spread(., key =DiscClass, value = count, fill = 0 ) %>% 
#   mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
#   slice(c(1:13, 15:17, 14, 18:20)) %>%
#    bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
#   SemiDataStructure
# 
# 
# HaveringLONDATA <- read_excel("AIR12965P Informatiion provided by Council Tax.xlsx" ) %>%
#   rename(DiscClass = X__1) %>%
#   select(-Mawneys, -`Aveley & Uplands`, -Whalebone) %>%
#   gather(key = "ward", value = "counts", -DiscClass) %>%
#   spread(key= DiscClass, value = counts, fill = 0) %>%
#   mutate(Empty = rowSums(.[,c(5:6,14,17)]), LowUse = Empty+ `Second Home Class A`+ `Second Homes Class B`) %>% 
#   bind_cols(., wardnames %>% filter(grepl("Havering", LAD11NM))) %>%
#   SemiDataStructure
